---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DYNAMIC.IV

<!-- badges: start -->
<!-- badges: end -->

Sample size simulator for DYNAMIC-IV cohort A. This version calls the original 'BuyseTest' package via the 'Rcpp' interface.'WH' code is otherwise designed to maximize speed, for use in simulation studies. As such, input validation is minimal and the user is responsible for ensuring valid use.

## Installation

You can install the development version of DYNAMIC.IV from [GitHub](https://github.com/hongconsulting/DYNAMIC.IV) with:

``` r
remotes::install_github("hongconsulting/DYNAMIC.IV")
```

## Example: single-threaded

```{r example1}
library(DYNAMIC.IV)

print(WH_DYNAMIC_IV(n_max = 204,
                    p_arm0surv = 0.73, p_arm1surv = 0.70,
                    p_arm0tox1 = 0.25, p_arm1tox1 = 0.1,
                    p_arm0tox2 = 0.45, p_arm1tox2 = 0.05, p_LTFU = 0.1, 
                    recrate = 7.5, reps = 100))
```

## Example: chunked parallel

```{r example2}
library(DYNAMIC.IV)
library(parallel)

reps <- 1000
n_cores <- parallel::detectCores()
chunk_reps <- rep(ceiling(reps / n_cores), n_cores)
chunk_reps[length(chunk_reps)] <- reps - sum(head(chunk_reps, -1))
seeds <- seq_along(chunk_reps)

sims <- do.call(rbind, parallel::mclapply(seeds, function(i) {
  WH_DYNAMIC_IV(n_max = 204,
                p_arm0surv = 0.73, p_arm1surv = 0.70,
                p_arm0tox1 = 0.25, p_arm1tox1 = 0.1,
                p_arm0tox2 = 0.45, p_arm1tox2 = 0.05,
                p_LTFU = 0.1, recrate = 7.5, reps = chunk_reps[i],
                seed = seeds[i], echo = FALSE)
}, mc.cores = n_cores))
print(colSums(sims * rep(chunk_reps, times = 3))/reps)
```
