---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DYNAMIC.IV

<!-- badges: start -->
<!-- badges: end -->

Sample size simulator for NIHR502533. This version calls the original 'BuyseTest' package via the 'Rcpp' interface. The surrounding 'WH' code is designed to maximize speed for use in simulation studies. As such, input validation is minimal and the user is responsible for ensuring valid use.

## Installation

You can install the development version of NIHR502533 from [GitHub](https://github.com/hongconsulting/NIHR502533) with:

``` r
remotes::install_github("hongconsulting/NIHR502533")
```

## Cohort A: single-threaded

```{r example1}
library(NIHR502533)

print(WH_NIHR502533a(n_max = 204,
                    p_arm0surv = 0.73, p_arm1surv = 0.70,
                    p_arm0tox1 = 0.25, p_arm1tox1 = 0.1,
                    p_arm0tox2 = 0.45, p_arm1tox2 = 0.05, p_LTFU = 0.1, 
                    recrate = 7.5, reps = 100))
```

## Cohort A: chunked parallel

```{r example2}
library(NIHR502533)
library(parallel)

reps <- 1000
n_cores <- parallel::detectCores()
chunk_reps <- rep(ceiling(reps / n_cores), n_cores)
chunk_reps[length(chunk_reps)] <- reps - sum(head(chunk_reps, -1))
seeds <- seq_along(chunk_reps)

sims <- do.call(rbind, parallel::mclapply(seeds, function(i) {
  WH_NIHR502533a(n_max = 204,
                p_arm0surv = 0.73, p_arm1surv = 0.70,
                p_arm0tox1 = 0.25, p_arm1tox1 = 0.1,
                p_arm0tox2 = 0.45, p_arm1tox2 = 0.05,
                p_LTFU = 0.1, recrate = 7.5, reps = chunk_reps[i],
                seed = seeds[i], echo = FALSE)
}, mc.cores = n_cores))
print(colSums(sims * rep(chunk_reps, times = 3))/reps)
```

## Cohort B: 

```{r example3}
library(NIHR502533)
# print(WH_NIHR502533b(n_max = 19, 
#                p_arm0clear = 0.34, 
#                p_LTFU = 0.15, recrate = 7.5, reps = 1e5))
```
